%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Relevant Courses}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
 \iffalse
  \cventry
    {Department of Electrical Engineering} % Detail
    {Operating System (A)} % Title
    {NCKU} % Location
    {Sep. 2020 - Jan. 2021} % Date(s)
    {
    }
    
%---------------------------------------------------------
  \cventry
    {Department of Electrical Engineering} % Detail
    {Data Structures (A-)} % Title
    {NCKU} % Location
    {Feb. 2021 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {I implemented and analyzed various sorting algorithms, systematically evaluating their time complexity and space complexity to gain insights into their efficiency and performance.}
      \end{cvitems}
    }
  \fi
%---------------------------------------------------------
  \cventry
    {Department of Mechanical Engineering} % Detail
    {Object Oriented Programming And Its Applications (A)} % Title
    {NCKU} % Location
    {Sep. 2021 - Jan. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Develop an accounting application in C++ using object-oriented programming (OOP).}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Department of Computer Science and Information Engineering} % Detail
    {Analysis And Implementation of Embedded Operating Systems (A+)} % Title
    {NCKU} % Location
    {Feb. 2023 - Jun. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Using \href{https://www.freertos.org/}{FreeRTOS} to develop IoT environment sensing devices.}
        \item {Define packet format and facilitate communication between IoT devices using the LoRa technique.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Department of Computer Science and Information Engineering} % Detail
    {Computer Architecture} % Title
    {NCKU} % Location
    {Sep. 2023 - Jan. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {RISC-V instruction, datapath, pipeline, cache, multithreading and synchronization.}
        \item {Validate and analyze the performance of the assembly code I wrote using \href{https://github.com/sysprog21/rv32emu}{rv32emu} to enhance the original program and make comparisons.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\end{cventries}
